---
title: "Module 1: Quarto Basics"
output: learnr::tutorial
runtime: shiny_prerendered
description: "Test your understanding of Quarto basics for openwashdata package documentation"
resource_files:
  - github_usernames.csv
  - _github_username.Rmd
  - _participation.Rmd
  - _submission.Rmd
tutorial:
  id: "module1-quarto-basics"
---

```{r setup, include=FALSE}
library(learnr)
library(dplyr)
library(gapminder)
library(knitr)
library(gradethis)
library(learnrhash)
library(httr)

# Enable exercise checking
tutorial_options(
  exercise.eval = FALSE,
  exercise.checker = gradethis::grade_learnr
)

knitr::opts_chunk$set(echo = FALSE)

```

## Introduction

This quiz tests your understanding of Quarto basics for openwashdata package documentation. The quiz covers YAML headers, code chunks, and data analysis integration.

**Important**: Please enter your GitHub username below and click "Submit Quiz" at the end to record your completion.

```{r github-username, child='_github_username.Rmd'}
```

```{r participation, child='_participation.Rmd'}
```

## Section 1: Quarto Fundamentals

### Question 1: YAML Header

```{r yaml-question}
question("Which of the following is the correct YAML header for an openwashdata package README?",
  answer("`---`\n`output: html_document`\n`---`"),
  answer("`---`\n`output: github_document`\n`---`", correct = TRUE),
  answer("`---`\n`format: html`\n`---`"),
  answer("`---`\n`format: markdown`\n`---`"),
  allow_retry = TRUE,
  incorrect = "Think about what output format is typically used for GitHub README files.",
  correct = "Correct! The github_document output format is used for README files that will be displayed on GitHub."
)
```

### Question 2: pkgdown Configuration

```{r pkgdown-question}
question("What file is used to configure the pkgdown website for an openwashdata package?",
  answer("pkgdown.yml"),
  answer("_pkgdown.yml", correct = TRUE),
  answer("config.yml"),
  answer("_config.yml"),
  allow_retry = TRUE,
  incorrect = "The configuration file starts with an underscore and has a .yml extension.",
  correct = "Correct! The _pkgdown.yml file is used to configure pkgdown websites."
)
```

## Section 2: Code Chunks and Options

### Question 3: Code Chunk Options

```{r chunk-options-question}
question("Which chunk options would you use to hide both code and messages when loading tidyverse?",
  answer("`echo = TRUE, message = TRUE`"),
  answer("`echo = FALSE, message = FALSE`", correct = TRUE),
  answer("`include = TRUE`"),
  answer("`eval = FALSE`"),
  allow_retry = TRUE,
  incorrect = "In Quarto, you can use `#| echo: false` and `#| message: false` to hide code and messages.",
  correct = "Correct! Setting echo = FALSE hides the code and message = FALSE hides the messages."
)
```

### Question 4: Creating Tables

Use the gapminder dataset to create a summary table showing the average life expectancy by continent in 2007:

```{r create-table-setup}
library(dplyr)
library(gapminder)
library(knitr)
```

```{r create-table, exercise=TRUE, exercise.lines=10}
# Create a summary table of average life expectancy by continent for 2007
# Your code here
```

```{r create-table-hint-1}
# Start by filtering for year 2007
gapminder %>%
  filter(year == 2007)
```

```{r create-table-hint-2}
# Then group by continent and calculate mean
gapminder %>%
  filter(year == 2007) %>%
  group_by(continent) %>%
  summarise(avg_life_exp = mean(lifeExp))
```

```{r create-table-solution}
gapminder %>%
  filter(year == 2007) %>%
  group_by(continent) %>%
  summarise(avg_life_exp = mean(lifeExp)) %>%
  knitr::kable(digits = 1)
```

```{r create-table-check}
grade_this_code()
```

## Section 3: Data Analysis Integration

### Question 5: Inline Code

Calculate the mean GDP per capita for Switzerland in 2007:

```{r inline-code-setup}
library(dplyr)
library(gapminder)
```

```{r inline-code, exercise=TRUE, exercise.lines=10}
# Calculate Switzerland's GDP per capita in 2007
swiss_gdp_2007 <- gapminder %>%
  filter(country == "Switzerland", year == 2007) %>%
  pull(gdpPercap)

# Display the result
paste("Switzerland's GDP per capita in 2007 was $", 
      format(swiss_gdp_2007, big.mark = ","), sep = "")
```

```{r inline-code-solution}
swiss_gdp_2007 <- gapminder %>%
  filter(country == "Switzerland", year == 2007) %>%
  pull(gdpPercap)

paste("Switzerland's GDP per capita in 2007 was $", 
      format(swiss_gdp_2007, big.mark = ","), sep = "")
```

```{r inline-code-check}
grade_this_code()
```

### Question 6: Data Visualization

Create a line plot showing the life expectancy over time for African countries with a population greater than 30 million in 2007:

```{r visualization-setup}
library(dplyr)
library(gapminder)

# Identify African countries with population > 30 million in 2007
large_african_countries <- gapminder %>%
  filter(continent == "Africa", year == 2007, pop > 30000000) %>%
  pull(country)
```

```{r visualization, exercise=TRUE, exercise.lines=15}
# Create the plot
# Your code here
```

```{r visualization-hint-1}
# Start by filtering for the large African countries
gapminder %>%
  filter(country %in% large_african_countries)
```

```{r visualization-hint-2}
# Then create a ggplot with appropriate aesthetics
gapminder %>%
  filter(country %in% large_african_countries) %>%
  ggplot(aes(x = year, y = lifeExp, color = country))
```

```{r visualization-solution}
gapminder %>%
  filter(country %in% large_african_countries) %>%
  ggplot(aes(x = year, y = lifeExp, color = country)) +
  geom_line() +
  labs(title = "Life Expectancy Over Time",
       subtitle = "African countries with population > 30 million in 2007",
       x = "Year",
       y = "Life Expectancy (years)",
       color = "Country") +
  theme_minimal()
```

```{r visualization-check}
grade_this_code()
```

```{r submission-section, child='_submission.Rmd'}
```

## Summary

This quiz covered essential Quarto skills for openwashdata package documentation:

1. **YAML Headers**: Configuring document output formats
2. **Code Chunks**: Managing code execution and output display
3. **Data Integration**: Combining narrative text with R analysis
4. **Visualization**: Creating informative plots within documents

Remember that Quarto documents can be rendered to multiple formats, making them ideal for creating both package documentation and interactive tutorials like this one!